---
title: "Assignment_5"
author: "Livia Costa"
date: "2024-03-13"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
#Write a function that takes a vector fish names and always returns three items: The most commmon fish, the rarest fish, the total number of fish.
#' Fish catch data
#'
#' Data on a catch of fish from Santa Barbara
#'
#' @format A dataframe with 100 rows 1 column
#' \itemize{
#'   \item fish name
#'   }
#'@source \url{http://www.sblter.ed/}
"fish"

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
source("../R/fish_analysis.R")

```


```{r}
# Set working directory to the correct path
setwd("/Users/lmcosta/ESM262/Data")

# Check current working directory
getwd()

# Read the fish.txt file
file_path <- "fish.txt"

if (file.exists(file_path)) {
  fish_data <- readLines(file_path)
  
  # Use the fish_analysis function
  result <- fish_analysis(fish_data)
  
  # Display the results
  cat("Most Common Fish:", result$most_common_fish, "\n")
  cat("Rarest Fish:", result$rarest_fish, "\n")
  cat("Total Number of Fish:", result$total_fish, "\n")
} else {
  stop("File not found: fish.txt")
}
```
```{r}
#Function to calculate fish summary
fish_summary <- function(fish_vector) {
  #Converting the vector to a data frame
  fish_data <- data.frame(fish = fish_vector)
  #Calculating the frequency of each fish species
  fish_frequency <- table(fish_data$fish)
  # Calculate the rarest and most common fish
  rarefish <- names(which.min(fish_frequency))
  commonfish <- names(which.max(fish_frequency))
  
  # Calculate the total number of fish
  nfish <- length(fish_vector)
  
  # Return the results
  result <- list(
    rarefish = rarefish,
    commonfish = commonfish,
    nfish = nfish
  )
  
  return(result)
}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
